Test susieI using chr17 to 22

### 2020-09-18 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
BF

@@

>>>>

# Regional BF distribution
mean BF of both SNPs and genes in region as the regional BF.

```{r rBF twas, fig.height=6, fig.width=6}
rpipf <- paste0(simdatadir, simtag, ".rBF.txt")

a <- read.table(rpipf, header = T)
a.c <- a[a$nCausal > 0, ]

par(mfrow=c(2,1))
h1 <- hist(a$rBF, breaks = 5000, xlab = "PIP", main = "regional BF distribution-all", col = "grey", xlim = c(0,10)); grid()
h2 <- hist(a.c$rBF, breaks = h1$breaks, xlab = "PIP", main = "regional BF distribution-causal", col = "salmon",xlim = c(0,10));grid()
```

@@

## Regions: TWAS BF

* Regions: regional TWAS BF > 2

```{r param 5, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config12.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config12.susieI.txt")
